Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-30 astronum_2018/astronum-xrb.tex
Remove explicit References section.
As the bibliography command puts one in on my system, so it duplicates.

Also a couple of tiny typos.

The 2D calculations shown in the previous section require about 10k
node-hours of computational time to get to about 10~ms (running
on the Edison machine at NERSC).  We expect qualitatively different
results in 3D calculations: for example, the shear from the hurricane structure
acting along the flame front may cause instabilities that can affect the flame
propagation.
With our current simulation methodology,
a 3D version of this calculation is estimated to require 10M node-hours
or more---this is about the size of an annualallocation.
%Additionally, this is still with the boosted flame, but we expect that once the flame is developed, the boosting will not be as critical, due to hydrodynamic effects.
This simulation covers less than
1\% of the neutron star surface, so a fully resolved calculation of
burning over the entire neutron star is out of reach: a naive scaling
calculation suggest that 15 years of Moore's Law improvements are required.
%
% The calculation above is
% log_2 [ (4 pi 10^2) / (1.23^2) ] * 1.5
% for a NS of 10km radius vs the computational domain of 1.23km^2
%

@@

\section*{References}

>>>>

The 2D calculations shown in the previous section require about 10k
node-hours of computational time to get to about 10~ms (running
on the Edison machine at NERSC).  We expect qualitatively different
results in 3D calculations: for example, the shear from the hurricane structure
acting along the flame front may cause instabilities that can affect the flame
propagation.
With our current simulation methodology,
a 3D version of this calculation is estimated to require 10M node-hours
or more---this is about the size of an annual allocation.
%Additionally, this is still with the boosted flame, but we expect that once the flame is developed, the boosting will not be as critical, due to hydrodynamic effects.
This simulation covers less than
1\% of the neutron star surface, so a fully resolved calculation of
burning over the entire neutron star is out of reach: a naive scaling
calculation suggests that 15 years of Moore's Law improvements are required.
%
% The calculation above is
% log_2 [ (4 pi 10^2) / (1.23^2) ] * 1.5
% for a NS of 10km radius vs the computational domain of 1.23km^2
%

@@

%\section*{References}
